### 2023-10-17 cv/cv-body.tex
DOI

\hypertarget{professional-experience}{%
\section{Professional experience}\label{professional-experience}}

@@

\hypertarget{education}{%
\section{Education}\label{education}}

@@

\hypertarget{preprints}{%
\section{Preprints}\label{preprints}}

@@

\hypertarget{publications}{%
\section{Publications}\label{publications}}

@@

of Marine Science.

@@

(\href{http://icesjms.oxfordjournals.org/content/early/2014/04/09/icesjms.fsu055.full.pdf?keytype=ref\&ijkey=NEXmZIkz3289u3z}{PDF}).

@@

(\href{http://www.plosone.org/article/fetchObject.action?uri=info\%3Adoi\%2F10.1371\%2Fjournal.pone.0092725\&representation=PDF}{PDF}).

@@

(\href{http://www.plosone.org/article/fetchObject.action?uri=info\%3Adoi\%2F10.1371\%2Fjournal.pone.0078041\&representation=PDF}{PDF}).

@@

(\href{http://www.plosone.org/article/fetchObject.action?uri=info\%3Adoi\%2F10.1371\%2Fjournal.pone.0014735\&representation=PDF}{PDF}).

@@

\hypertarget{peer-reviewed-government-reports}{%
\section{Peer-reviewed government
reports}\label{peer-reviewed-government-reports}}

@@

\hypertarget{technical-reports}{%
\section{Technical Reports}\label{technical-reports}}

@@

\hypertarget{awards-and-scholarships}{%
\section{Awards and scholarships}\label{awards-and-scholarships}}

@@

\hypertarget{software}{%
\section{Software}\label{software}}

@@

\hypertarget{selected-first-author-invited-conference-presentations}{%
\section{Selected first-author invited conference
presentations}\label{selected-first-author-invited-conference-presentations}}

@@

\hypertarget{teaching}{%
\section{Teaching}\label{teaching}}

@@

\hypertarget{working-groups-and-workshops}{%
\section{Working groups and
workshops}\label{working-groups-and-workshops}}

@@

\hypertarget{reviewing}{%
\section{Reviewing}\label{reviewing}}

>>>>

\section{Professional experience}\label{professional-experience}

@@

\section{Education}\label{education}

@@

\section{Preprints}\label{preprints}

@@

\section{Publications}\label{publications}

@@

of Marine Science. \url{https://doi.org/10.1093/icesjms/fsad155}.

@@

(\href{http://icesjms.oxfordjournals.org/content/early/2014/04/09/icesjms.fsu055.full.pdf?keytype=ref&ijkey=NEXmZIkz3289u3z}{PDF}).

@@

(\href{http://www.plosone.org/article/fetchObject.action?uri=info\%3Adoi\%2F10.1371\%2Fjournal.pone.0092725&representation=PDF}{PDF}).

@@

(\href{http://www.plosone.org/article/fetchObject.action?uri=info\%3Adoi\%2F10.1371\%2Fjournal.pone.0078041&representation=PDF}{PDF}).

@@

(\href{http://www.plosone.org/article/fetchObject.action?uri=info\%3Adoi\%2F10.1371\%2Fjournal.pone.0014735&representation=PDF}{PDF}).

@@

\section{Peer-reviewed government
reports}\label{peer-reviewed-government-reports}

@@

\section{Technical Reports}\label{technical-reports}

@@

\section{Awards and scholarships}\label{awards-and-scholarships}

@@

\section{Software}\label{software}

@@

\section{Selected first-author invited conference
presentations}\label{selected-first-author-invited-conference-presentations}

@@

\section{Teaching}\label{teaching}

@@

\section{Working groups and
workshops}\label{working-groups-and-workshops}

@@

\section{Reviewing}\label{reviewing}
